\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

%----------------------------------------------------------------------------------------
% Contact Information
%----------------------------------------------------------------------------------------

\name{Christian Sakai} % Your name
\address{+1 (347) 430-3398 \\
    Jersey City, New Jersey, US \\
    \href{mailto:christianmsakai@gmail.com}{christianmsakai@gmail.com}
}
\address{\href{https://github.com/Exegetech}{github.com/Exegetech} \\
    \href{https://linkedin.com/in/christiansakai}{linkedin.com/in/christiansakai} \\
}

\begin{document}

%----------------------------------------------------------------------------------------
% Professional Summary
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Summary}

{Frontend Engineer with deep knowledge of the web stack and years of experience working in small and large teams to develop high-performance, interactive, user-friendly, visually-appealing and feature-rich web applications.}

\end{rSection}

%----------------------------------------------------------------------------------------
% Work Experience
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\textbf{Senior Frontend Engineer (Contract)} \hfill July 2024 --- Current \\
Oxio \hfill \textit{New York City, NY}
\begin{itemize}
    \item {Re-engineered the frontend repo into monorepo, established efficient and robust CI pipeline and increased E2E throughput by 200\%}
\end{itemize}

\textbf{Senior Frontend Engineer} \hfill May 2022 --- Oct 2023 \\
Old Mission Capital \hfill \textit{New York City, NY}
\begin{itemize}
    \item {Engineered a high-performance GUI dashboard for equity portfolio that handled 1000 table updates per second and up to a billion dollars per month using React, WebSocket, Web Worker, AG Grid, Protobuf and OpenFin.}
    \item {Upgraded monorepo build system workflow, resulted in 300\% CI throughput by using Bazel, PNPM and analysis of the webpack compiler.}
    \item {Improved team efficiency by mentoring junior engineers in best practices and overview of the JavaScript ecosystem.}
    \item {Built dependency graph and Gantt chart visualization for a job scheduler GUI that was utilized by the entire engineering team using React and Highcharts.}
\end{itemize}

\textbf{Senior Software Engineer} \hfill Apr 2020 --- Apr 2022 \\
Bloomberg LP \hfill \textit{New York City, NY}
\begin{itemize}
    \item {Engineered an email analysis dashboard which was used by the entire cybersecurity department by using Angular, TypeScript, ElasticSearch and MongoDB.}
    \item {Built a tracking analysis dashboard by using React, TypeScript, Python, Flask, MongoDB and Redis.}
\end{itemize}

\textbf{Fullstack Platform Engineer} \hfill Feb 2019 --- Apr 2020 \\
Lifion by ADP \hfill \textit{New York City, NY}
\begin{itemize}
    \item {Designed and built i18n pipeline for flagship end-user facing apps by using React and JavaScript.}
    \item {Built a service to streamline ETL pipeline transformation using TypeScript, NodeJS, JavaScript and Go.}
\end{itemize}

\textbf{Frontend Engineer} \hfill Jul 2018 --- Mar 2019 \\
ITN Networks \hfill \textit{New York City, NY}
\begin{itemize}
    \item {Enhanced the company's front end codebase with over 1.5 million lines of code with 10 other engineers using React and TypeScript.}
    \item {Improved code quality by integrating Cypress testing automation and mentoring QA engineers in e2e testing best practices.}
\end{itemize}

% \textbf{Fullstack Software Engineer} \hfill Oct 2016 --- Mar 2018 \\
% IrisVR Inc. \hfill \textit{New York City, NY}
% \begin{itemize}
%     \item {Built the flagship web and desktop client using React, Redux, Webpack, Electron and JavaScript.}
% \end{itemize}
%
% \textbf{Co-founder \& Fullstack Software Engineer} \hfill Mar 2015 --- Dec 2015 \\
% Ninthbeat Inc. \hfill \textit{New York City, NY}
% \begin{itemize}
%     \item {Built the flagship web and mobile marketplace app for musicians to buy and sell their used musical instruments.}
% \end{itemize}

%----------------------------------------------------------------------------------------
% Skills
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & JavaScript, TypeScript, HTML, CSS, SASS, Go, Python \\
Framework & React, Angular, Express, Jest \\
Technologies & Web Workers, WebSocket, WebSocket, Redux, AG Grid, Highcharts, Protobuf, NodeJS, Webpack, Docker, Bazel, OpenFin, Electron \\
Databases & MongoDB, PostgreSQL \\
\end{tabular}\\

\end{rSection}

%----------------------------------------------------------------------------------------
% Education Section (Shift below Projects if your projects are substantial)
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\textbf{Master of Art, Computer Science}, Queens College \hfill {Aug 2016 --- May 2018}

\textbf{Master of Divinity, Theological Studies}, Alliance Theological Seminary \hfill {Aug 2010 --- May 2013}

\textbf{Bachelor of Engineering, Industrial Engineering}, Bina Nusantara University \hfill {Aug 2004 --- May 2008}

\end{rSection}

%----------------------------------------------------------------------------------------
% Projects
%----------------------------------------------------------------------------------------

% \begin{rSection}{Projects}

% \textbf{Role}, {Project Name} (\href{https://myproject.com}{myproject.com}) \hfill {MMM YYYY --- MMM YYYY}
% \begin{itemize}
%     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
%     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
% \end{itemize}

% \textbf{Role}, {Project Name} (\href{https://github.com/my-project}{github.com/my-project}) \hfill {MMM YYYY --- MMM YYYY}
% \begin{itemize}
%     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
%     \item \href{https://www.faangtechleads.com/resume/general-guidelines}{Action verb} + what you did + reason, outcome or quantified results. Talk about technologies used.
% \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% Awards
%----------------------------------------------------------------------------------------

% \begin{rSection}{Awards}

% \begin{itemize}
%     \item \textbf{ABC Hackathon} --- 1st place \hfill {MMM YYYY --- MMM YYYY}
%     \item \textbf{XYZ Competition} --- 2nd place \hfill {MMM YYYY --- MMM YYYY}
% \end{itemize}

% \end{rSection}

\end{document}
